### 2017-05-19 Manuscript/ms.tex
Working on restructuring intro

Dengue fever is a massive global public health burden, with millions of cases per year in Brazil alone (CITATION).  
Since the dengue virus (DENV) is vectored by the mosquito \textit{Aedes aegypti}, dengue fever is prevented primarily through mosquito surveillance and control programs \cite{Achee2015}.
Deploying these mosquito control measures effectively and efficiently requires a detailed understanding of how mosquito surveillance indices map to human disease risk.
For example contact tracing and residential spraying reduced disease risk in Cairns, Australia \cite{Vazquez-Prokopec2017}.
This approach ensures that the mosquitoes targeted by control are epidemiologically relevant, but the detailed data it requires potentially limits its utility for large-scale deployment.

More commonly, cities deploy mosquito control based on trap-based mosquito surveillance data.
For instance, the "MI-Dengue" system deployed throughout several cities in Brazil uses a grid of mosquito sticky-traps (MosquiTRAPs) for spatial prioritization of source reduction and larvicide application \cite{Eiras2009}.
Comparing cities with and without this system, \cite{Pepin2013} estimated that it prevented X cases and saved X dollars in economic losses from 20XX - 20XX.
Though this system has been effective, the mosquito indices and thresholds used to prioritize control efforts remain somewhat ad-hoc.
Using such surveillance data to efficiently target limited control resources requires a more detailed understanding of the relationship between the components of mosquito abundance measured by traps and disease risk.

@@

\begin{itemize}
\item Human movement \cite{Adams2009, Cosner2009a, Stoddard2009, Dalziel2013}
\item Disease risk possibly driven by high levels of contact with a relatively small proportion of the mosquito population \cite{Canyon1999}.
\end{itemize}

>>>>

Dengue fever is a massive global public health burden, with millions of cases per year in Brazil alone (CITATION).  
Since the dengue virus (DENV) is vectored by the mosquito \textit{Aedes aegypti}, dengue fever is prevented primarily through mosquito control programs \cite{Achee2015}.
Though eradication of \textit{Aedes aegypti} is infeasible, effectively targeted control interventions may still substantially reduce disease risk.

Cities deploy mosquito control based on trap-based mosquito surveillance data.
For instance, the "MI-Dengue" system deployed throughout several cities in Brazil uses a grid of mosquito sticky-traps (MosquiTRAPs) for spatial prioritization of source reduction and larvicide application \cite{Eiras2009}.
Comparing cities with and without this system, \cite{Pepin2013} estimated that it prevented X cases and saved X dollars in economic losses from 20XX - 20XX.
Though this system has been effective, the mosquito indices and thresholds used to prioritize control efforts remain somewhat ad-hoc.
Using such surveillance data to efficiently target limited control resources requires a more detailed understanding of the relationship between the components of mosquito abundance measured by traps and disease risk.

@@

\begin{itemize}
\item Human movement \cite{Adams2009, Cosner2009a, Stoddard2009, Dalziel2013}
\item Disease risk possibly driven by high levels of contact with a relatively small proportion of the mosquito population \cite{Canyon1999}.
\item Explicitly targeting mosquitoes that have been implicated in transmission through the use of contact tracing \cite{Vazquez-Prokopec2017}
\end{itemize}
